Spontaneous Similarity Judgements of Musical Tones played with Various Playing Techniques

### 2018-01-28 paper/lagrangeSpontaneousSimilarity2017.tex
title capitalization
the title should be changed (played, playing)
descrption -> description

% Title.
% ------
\title{Spontaneous Similarity Judgments of Musical Tones played with various Playing Techniques}

@@

To further study the outcomes of this experiment, we assume a two-step computational model of human perception, where the acoustic signal is fed to a statically designed processing unit that accounts for frequency and temporal modulations. The resulting features are then projected in a supervised manner so that the resulting descrption space matches the perceptual similarity judgments gathered in the second experiment. Numerical experiments show that the induced perceptual space is able to approximate perceptual data with satisfying accuracy.

>>>>

% Title.
% ------
\title{Spontaneous Similarity Judgements of Musical Tones played with Various Playing Techniques}

@@

To further study the outcomes of this experiment, we assume a two-step computational model of human perception, where the acoustic signal is fed to a statically designed processing unit that accounts for frequency and temporal modulations. The resulting features are then projected in a supervised manner so that the resulting description space matches the perceptual similarity judgments gathered in the second experiment. Numerical experiments show that the induced perceptual space is able to approximate perceptual data with satisfying accuracy.
